Digital economy in the UK: an evolutionary story

### 2023-10-27 paper/submission1/tranos2023.tex
presentation

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, frame hidden]}{\end{tcolorbox}}\fi

@@

This paper offers such a contribution: a geographical study illustrating
how a new technology that is the web diffused over space and time in the
UK at a high level of spatial granularity during the \(1996-2012\)
period. It does so by employing a novel source of big data which
captures the active engagement with web technologies during that period.
By addressing this empirical question this paper exemplifies how the
combination of data sources which escape the traditional social science
domain and adequate research methods can offer new contributions
regarding our understanding of technologies are diffused.

The motivation for this paper lies in the fact that there are various
stakeholders who are interested in knowing how new digital technologies
diffused over space and time and use this information to make
predictions regarding the diffusion of related \emph{future}
technologies. As per \citet{leibowicz2016representing}, historical
studies agree on the fact that ``technologies diffuse at different
times, at different rates, and to different extents in different places,
and can be significantly influenced by policies
\citep{victor1993}''.@meade2021modelling highlight that a variety of
actors have a direct interest in gaining such knowledge including
network equipment suppliers; network operators, regulatory and local
authorities. These processes and their effects very a lot between
scales: although the diffusion of a new technology might not be optimal
at a local level, it might be beneficial from a global perspective as it
might enable faster diffusion to less advantaged places
\citet{leibowicz2016representing}. Despite the spatial heterogeneity of
such diffusion mechanisms and the policy relevance, there are very
limited attempts in the literature to analyse the diffusion of new
digital technologies at a detailed geographical level.

To summarize the discussion, first, here the diffusion process is
selfperpetuating as initial use stimulates further use. Second, it
follows a disequilibrium path as the level of users is always lower than
the number of potential users (Stoneman 2002).

The criticisms are mainly based on the fact that although the approach
gives an idea of aggregate (industry or household) behaviour, it does
not focus on the individual's (firm or household) adoption process

\citet{morrill2020spatial} Spatial diffusion is the process by which
behavior or characteristics of the landscape change as a result of what
happens elsewhere earlier. Spatial diffusion is the spread of the
phenomenon, over space and timed, from limited origins

Compare dissusion with adoption

wilson201281 Early on in their lifecycle, new technologies are crude,
imperfect, and expensive (Rosenberg, 1994). New energy technologies are
attractive for their ability to perform a particular task or deliver a
new or improved energy service (Fouquet, 2010). This is often
circumscribed by a particular set of needs in a particular context: a
market `niche'. End-users in niche markets are generally less sensitive
to the effective price of the energy service provided or have a higher
willingness to pay for its performance advantages (Fouquet, 2010). Thus
initially, performance dominates cost competitiveness (Wilson and
Grubler, 2011). Market niches afford some protection from competitive
pressures, allowing technologies to be tested and improved in applied
settings, reducing uncertainties with performance or market demand (Kemp
et al., 1998). Costs may only fall substantively after an extended
period of commercial experimentation, concurrent with the establishment
of an industrial base and characteristic moves towards standardisation
and mass production (Grubler, 1998). The influence of accumulating
production experience on costs is captured by the concept of learning.

grubler1990rise The scale of spatial innovation diffusion is similar to
that of temporal diffusion models: hierarchically decomposed.

@@

\citet{perkins2005international} Theoretical models disagree as to why
firms adopt innovations at different times. Epidemic models emphasize
information (Griliches 1957). Certain firms are hypothesized to adopt
earlier because they come into contact with, and learn from, adopters of
the new technology before others. Economic models, on the other hand,
predominantly emphasize firm heterogeneity (Ireland and Stoneman 1986).
Firms adopt technologies at different times because they differ with
respect to various organizational and environmental variables
influencing the economic returns from adoption (Blackman 1999).

Either way, the strong assumption is that developing countries can
acquire modern technology innovated in developed economies, often at a
fraction of the original research and development (R\&D) costs, thereby
leapfrogging many decades of technological progress (Teece 2000).

The first involves a country's geographical location. Recent empirical
work suggests that diffusion is `'geographically localized'' (Globerman,
Kokko, and Sjo¨holm 2000; Keller 2002; Milner 2003) in that a technology
diffuses faster in a country where it is already more widely diffused in
neighboring countries. Underlying these regional effects are contagion
and contact with prior users or producers of technology.

\citet{ding2010modeling} Rogers (1995) characterized early adopters as
knowledgeable risk takers. Griliches (1957) looked at the rate of return
for early adopters and characterized them as profit maximizers. The
geographer Hagerstrand (1967) was focusing on the character of early
adopters in the transmittal process that produces follow-on participants
in the process. Space was treated as a contiguity system with embedded
characteristics producing barrier elements to the diffusion process.

\citet{ding2010modeling} REVIEW ON Technological Diffusion

\citet{perkins2011internet} Two main mechanisms are identified in the
literature to explain diffusion: (1) epidemic-type dynamics whereby
contact with previous adopters stimulates uptake as po tential adopters
learn about a new innovation; and (2) economic-type mechanisms whereby
potential users adopt a new innovation as it be comesmore profitable,
useful, or valuable, with uptake characteristically spreading as costs
be come lower, performance improves, or the po tential uses of the
innovation grow over time.

To this extent, our results contribute to a growing body of work that
has sought to caution against claims about the supposed novelty of the
Internet and the suggestion that it is somehow different.

@@

MAYBE SKIP THIS??

\citet{beardsell1999spatial} To characterize evolution of the computer
industry, we examine the distribution of relative employment across
cities in 1977 and how that distribution changes over time to 1992

There is no tendency of relative size distributions of urban computer
employment to collapse, go bimodal, or fully spread. Overall computers
exhibit some turbulence, with dramatic big winners and losers among
cities. In attracting or repelling an industry, urban heterogeneity is
important. Large, well educated cities near San Jose have much greater
chances of attracting high-tech employment and less of losing it

\citet{bednarz2020pulled} spatial innovation diffusion By using Bayesian
survival models with time-dependent data of wind turbine deployment and
firm foundation for 402 German regions between the years 1970 and 2015,
we show that the spatial evolution of the German wind energy industry
was more strongly influenced by local demand-- pull than local
supply--push processes.

The industry's initial locations are distributed relatively arbitrarily
and unpredictably, as their needs in terms of resources and skills are
diverse and distinct from the older existing industries (Boschma and
Lambooy, 1999). Consequently, emerging industries are characterized by
relatively high degrees of freedom in terms of location. In later
extensions of the concept, the assumption of the randomness of locations
was revised with greater importance assigned to regional conditions
(Boschma and Lambooy, 1999; Fornahl et al., 2012).

\citet{perkins2005international} analyze whether the rate at which new
producer technologies diffuse is significantly influenced by (1)
latecomer advantage and (2) engagement with the global economy via trade
and foreign investment

Indeed, precisely because of these latecomer advantages, developing
countries1 are believed to be well placed to catch up with developed
ones (Gerschenkron 1962; Abramovitz 1986).

\citet{fritsch2015new} analyze the spatial diffusion of laser technology
research in West Germany from 1960, when this technology began, until
2005.

\citet{perkins2011internet}

\citet{lengyel2020role} We see that the OSN spread almost exclusively
from the original location (the capital Budapest, with an order of
magnitude more inhabitants than the next size town) to various parts of
the country in the early phase of the life-cycle. Later, diffusion
became less mono-centric and other towns also emerged as spreaders. Our
findings support the idea that spreading initially happens to large
distances and becomes more local over time. This is illustrated and
discussed later in Figure 2I.

\citet{PAPAGIANNIDIS2015308}

\citet{leibowicz2016representing} for energy There is no generally
accepted theory that explains diffusion rate heterogeneity across
technologies, but several factors are considered important. Greater unit
scale and larger market size contribute to slower diffusion.
Requirements for interrelated technologies or complex infrastructures
also hinder the diffusion process (Grubler, 2012).

Mobile phones benefited from early deployment in recreational boats and
automobiles, where the traditional competitor was not a viable option.
In the early stages of diffusion, performance is a more important driver
of adoption than cost competitiveness. Typically, significant cost
reductions only occur once the technology reaches a deployment level
capable of supporting standardization and mass production (Wilson,
2012).

\citet{leibowicz2016representing} Empirical evidence supports the
validity of Schmidt's Law over a wide range of technologies, time
periods, and geographical contexts. A recent meta-analysis of technology
up-scaling found that diffusion accelerated moving from the core to the
rim and periphery for technologies as diverse as natural gas power, oil
refineries, and automobiles (Wilson, 2009). One historical example that
conforms particularly well to Schmidt's Law is the diffusion of coal
power in Europe (Grubler, 2012). England emerged as the core region for
coal power because it had legal and economic institutions that
incentivized scientific pursuits, domestic coal reserves, and a clear
industrial motivation to replace water power with coal. \ldots{}

\citet{ding2010modeling} model the spatial diffusion of mobile
telecommunications in China as well as its determinants. regional
socioeconomic characteristics play an important role in determining the
timing, speed, and level of mobile telecommunications diffusion in China

\citet{bento2018time} explore What determines the duration of formative
phases for energy innovations in different markets? We are interested
both in initial markets (also: core, lead, first mover, early adopter)
where formative phases prepare technologies for mass commercialization,
and in follower markets (also: periphery, lag, late adopter) where
accelerated formative phases may benefit from diffusion and spillovers.

@@

@@

\renewcommand\refname{References}
  \bibliography{./paper/submission1/bibliography}

>>>>

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, breakable, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, enhanced, interior hidden]}{\end{tcolorbox}}\fi

@@

This paper offers such a contribution: a geographical study illustrating
how a new technology that is the web diffused over space and time in the
UK at a high level of spatial granularity during the \(1996-2012\)
period. It does so by employing a novel source of big data which
captures the active engagement with web technologies during that period.
By addressing this empirical question this paper exemplifies how the
combination of data sources which escape the traditional social science
domain and adequate research methods can offer new contributions
regarding our understanding of how new technologies diffuse.

The motivation for this paper lies in the fact that there are various
stakeholders who are interested in knowing how new digital technologies
diffused over space and time and use this information to make
predictions regarding the diffusion of related \emph{future}
technologies. As per \citet{leibowicz2016representing}, historical
studies agree on the fact that ``technologies diffuse at different
times, at different rates, and to different extents in different places,
and can be significantly influenced by policies \citep{victor1993}''.
\citet{meade2021modelling} highlight that a variety of actors have a
direct interest in gaining such knowledge including network equipment
suppliers; network operators, regulatory and local authorities. These
processes and their effects very a lot between scales: although the
diffusion of a new technology might not be optimal at a local level, it
might be beneficial from a global perspective as it could lead to faster
diffusion to less advantaged places \citep{leibowicz2016representing}.
Despite the spatial heterogeneity of such diffusion mechanisms and the
policy relevance, there are very limited attempts in the literature to
analyse the diffusion of new digital technologies at a detailed
geographical level.

Technological diffusion, which is by definition an aggregated process,
can be discussed in parallel with individual adoption mechanisms. On the
one hand, \citet{rogers2010diffusion} identifies early adopter of new
technologies as `knowledgeable risk takers' and \citet{griliches1957} as
`profit maximisers' \citep{ding2010modeling}. Such individual agents are
rewarded because of their attitude towards new technologies and
innovations. On the other hand, \citet{perkins2011internet} attribute
diffusion to two processes: (i) epidemic-like mechanisms, which are
governed by distance, proximity and social interactions, and (ii) by
economic mechanisms as new innovations are adopted by users as they
become more profitable, valueable and useful.

This paper focuses on the diffusion of the web as new technology during
the \(1996-2012\) period. This was an exciting period for digital
technologies as it corresponds with the commercialisation of the
internet and, consequently, its almost universal adoption. The reader is
reminded that it was only in 1994 when Netscape Navigator was
introduced, a year before Microsoft's Internet Explorer \footnote{\url{https://www.theguardian.com/global/2015/mar/22/web-browser-came-back-haunt-microsoft}}.
Also, only \(9\) per cent of UK's households had access to the internet
in \(1998\) \citep{ons2018} and during that period that web included
mostly static webpages, there were no social media and web browsing was
happening exclusively from desktop PCs as there were no smartphones
\citep{tranosuk}. Hence, it is fair to say that the study period
captures the very early stages of the diffusion on a new technology that
is the web. This is key point in the lifecycle of a new technology.
Firstly, during this period new technologies are expensive, crude and
imperfect \citep{rosenberg1994exploring, wilson201281}. A simple
comparison between Web 1.0 and Web 3.0 applications clearly illustrates
this \citep{tranos2020social}. During this period the performance of a
new technology is the main attraction and not the cost to access and use
it \citep{wilson2011lessons} There is a broader theoretical discussion
in the literature regarding the motivation behind early adoption. As
summarised by \citet{perkins2005international}, on the one hand,
epidemic models highlight the role of interpersonal contacts as a way
for new technologies to diffuse. On the other hand, economic models
underline the importance of heterogeneity. Different firms have
different structures and business plans, which define the potential
economic returns of the adoption of a new technology and, therefore, the
choice to adopt a new technology becomes an individual option. From a
broader and evolutionary perspective, initial conditions are essential
for the creation and evolution of path-dependent technological
development trajectories \citep{neffke2011regions, simmie2014new}. This
argument is even more relevant when the focus is on Information and
Communication Technologies (ICT) because of the commonly found lag
between investment and economic returns as reflected in the Solow
paradox \citep{acemoglu2014return, brynjolfsson2018artificial}.

Importantly, the data used here depicts the \emph{active} engagement
with the web as it contains all the commercial websites archived by the
Internet Archive \footnote{\href{See\%20https://archive.org/}{https://archive.org/}.}
that include a mention to at least one valid UK postcode in the web
text. Websites are identified as commercial ones if they are part of the
.co.uk second level domain (SLD). Also, the act of of creating a website
is understood here as active engagement with the web vis-à-vis the more
passive act of browsing the web or having an internet connection
\citep{tranosuk}. Previous studies have focused mostly on more passive
notions of engaging with digital technologies such as internet adoption
and internet speeds
\citep[e.g.][]{blank2018local, riddlesden2014broadband}.

@@

@@

Geographical diffusion is a synthesis of different processes. On the one
hand, we can identify purely spatial or, in other words, contagious
processes. Adjacency and, more broadly, distance are the key drivers of
diffusion. This perspective draws similarities with epidemics:
innovation just like pathogens spreads because of contagion and,
consequently, proximity and exposure \citep{hivner2003facilitating}. On
the other hand, we can identify hierarchical processes. Instead of
horizontal distance-based diffusion mechanisms, the top-down hierarchy
of urban systems drives diffusion. In reality, the synthesis of these
two processes represents how new technologies diffuse over space and
time \citep{morrill2020spatial}.

These ideas were firstly introduced by Torsten Hägerstrand and his
thesis entitled `Innovation Diffusion as a Spatial Process'
\citep{hagerstrand1968innovation}. Hägerstrand was the first one to
identify diffusion as a geographical process. The starting point was the
idea that diffusion is based on passing information through social
networks, which themselves tend to be defined by geography. Hence, he
identified the `neighbourhood' effect of how information, and
consequently, innovation diffuse. He used agricultural innovations to
test and model his ideas using Monte Carlo simulations. Hägerstrand also
incorporated the role of hierarchy and how some phenomena maybe firstly
adopted in larger cities and then diffuse to second tier ones. This is a
sequential instead of a simultaneous process, which resembles the
`lead-lag' spatial acceleration effect in market research
\citep{bento2018time, PERES201091}. Hägerstrand maybe more widely known
for highlighting the role time plays in the diffusion of innovations: an
early-pioneering period, a middle fast accelerating period and a final
saturation one {[}\citet{morrill2020spatial}.

The temporal dimension was further explored by Everett Rogers and his
seminal work on `Diffusion of Innovations' \citep{rogers2010diffusion}.
Rogers being a sociologist his work focused not on the diffusion of
innovations over space and time, but instead on the adoption of new
technologies and innovations by individuals and the individual
mechanisms that drive the decisions behind adoption. He identified five
groups of individuals regarding their adoption speed: innovators, early
adopters, early majority, late majority and laggards. Key mechanism of
diffusion and adoption is always communication and how knowledge is
transferred within a social system. Therefore, all approaches agree on
the S-shaped diffusion and cumulative adoption pattern
\citep{grubler1990rise}.

Schmidt's Law empirically illustrates a similar pattern. \emph{Core} and
usually highly agglomerated regions is where new technologies are
invented and commercially deployed {[}\citet{grubler1990rise};
grubler1990rise{]}. This is where the first adopters tend to be based.
Then, technologies spread to the \emph{rim} and eventually to the
\emph{periphery}. Although adoption pace might be higher when new
technologies finally arrive to the periphery, the saturation levels
there may never reach the ones in the core because of the lack of
infrastructure or other necessary institutions
\citep{leibowicz2016representing}. \citet{grubler1990rise} effectively
summarises the three key characteristics of the spatial diffusion
process: (i) the cumulative level of adoption follows an S-shaped
pattern just like purely temporal models; (ii) diffusion is shaped by a
hierarchy effect in a form of a centrifugal force: from core to
periphery; and (iii) diffusion is also shaped by distance and a
neighbourhood effect and contaminate nearby locations.

The remaining of this section reviews empirical studies which analysed
the diffusion on new technologies over space and time. Although the
spatial dimension is present in most of the following studies, the level
of spatial detail is almost always more coarse than the one adopted
here. To begin with \citet{beardsell1999spatial} studied the evolution
of the computer industry in \(317\) US metro areas during the
\(1977-1992\) period using employment data. Their analysis indicated
that the relative size distribution holds for urban computer employment
and also urban heterogeneity is essential in explaining this
distribution. \citet{bednarz2020pulled} focused on wind turbines and
modelled their spatial diffusion across \(402\) German regions during
\(1970-2015\). Their key finding is that local demand than local supply
was the main driving factor.

At a global scale \citet{perkins2005international} analyzed if the
diffusion rate of new technologies is driven by a latecomer advantage
and the engagement with the global economy via foreign direct
investments and trade. Their results illustrate that indeed latecomers
and developing countries experience diffusion of new technologies more
rapidly than early adopter and developed countries. At the same scale,
\citet{perkins2011internet} explored whether the adoption of previous
communication technologies that is mail, telegrams and telephones was
shaped by similar socioeconomic factors as the internet. Their results
indicated common patterns regarding the drivers behind the adoption of
different communication technologies.

Turning to studies that share more technological and scalar similarities
with this paper, \citet{ding2010modeling} modelled the spatial diffusion
of mobile telecommunications across regions in China. Their analysis
indicated that socioeconomic characteristics are important determinants
of the timing, speed and the level of mobile diffusion within China.
Using data from a Hungarian online social network,
\citet{lengyel2020role} analysed its adoption and the churn at a very
granular spatial level. Their results are in agreement with early
theoretical and empirical contributions reviewed here: assortativity,
urban scaling and distance are the key drivers of spatial diffusion. At
a global scale \citet{PAPAGIANNIDIS2015308} modelled the diffusion of
different web technologies technologies and practices. Interestingly,
they did so by using similar, but less extensive data as the one used
here. Their analysis illustrated how the diffusion of different web
technologies and practices follow an S-shaped pattern as well as the
different diffusion rates of the different technologies and practices.

@@

For instance, we can approximate digital economic activities in a region
by measuring the volume of commercial webpages by considering only
.co.uk websites, which are dedicated to commercial activities (Thelwall,
2000). Such commercial websites are used to exchange information,
support online transactions and share opinions (Blazquez \& Domenech,
2018). Although nothing prevents a UK-based company from adopting a
generic TLD such as.com and, indeed, such cases escape our data, we do
not expect that such omissions could affect our results given the
popularity of the .uk ccTLD: UK consumers prefer to visit a .uk website
when they are searching for products or services (Hope, 2017); and
anecdotal evidence indicates that during the first half of 2000, three
.co.uk domains were registered every minute (OECD, 2001). Also, as Table
1 demonstrates, .co.uk was the most popular SLD under the .uk ccTLD in
2000. Hence, we use the total volume of all the archived webpages in a
region as a proxy for the level of digitization. We start the analysis
by focusing on commercial webpages (.co.uk).

@@

\renewcommand\refname{References}
  \bibliography{bibliography}

### 2023-10-27 presentations/web_diffusion.Rmd
presentation

::: {style="margin-left: 50px !important; text-align:left !important"}
-   Introduction
-   Web data
-   Spatial analysis
-   S-shaped diffusion curves
-   Rank dynamics
-   Conclusions <br> <br>
    [etranos.info/post/gceg2022](https://etranos.info/post/gceg2022/)
:::

@@

-   Geographers used to be interested in diffusion

-   @hagerstrand1968innovation

-   Passed the torch to economists and sociologists

-   Why? Lack of granular data:

@@

-   Observe commercial websites 1996 - 2012

-   Geolocate to a unique location

-   Geolocate to multiple locations

@@

![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png)

@@

![](C:/Users/nw19521/OneDrive%20-%20University%20of%20Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png)

@@

## Spatial attributes

> **Neighborhood effect**: diffusion proceeds outwards from innovation
> centers, first "hitting" nearby rather than far-away locations
> [@grubler1990rise]

@@

-   Website density regressions

@@

```{r moransi_la, results='asis'}
path.in <- paste0(path, "/outputs/morani_la.csv")

@@

```{r, eval=T, moransi_oa, results='asis'}
path.in <- paste0(path, "/outputs/morani_oa.csv")
# read.csv(path.in) %>% dplyr::select(year, morani) %>% 
#   rename('Moran\'s I' = morani,
#          Year = year) %>% 
#   arrange(Year) %>% 
#   kable(digits = 3, 
#         label = "Moran\'s I per year, Output Areas") %>% 
#     kable_classic(full_width = F, html_font = "Cambria")

@@

```{r lisa_la, results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/")

@@

```{r lisa_oa, eval=T,results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/")

@@

```{r b_London_la, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/b_dist_london_la.png")
knitr::include_graphics(path.image)
```

@@

```{r b_London_oa, eval=T, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/b_dist_london_oa.png")
knitr::include_graphics(path.image)
```

@@

```{r b_city_la, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/b_dist_city_la.png")
knitr::include_graphics(path.image)
```

@@

```{r b_city_oa, eval = T, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/b_dist_city_oa.png")
knitr::include_graphics(path.image)
```

@@

```{r b_centre_la, message=FALSE}
#, out.height= "60%", out.width="60%"
path.image <- paste0(path, "/outputs/b_dist_centre_la.png")
knitr::include_graphics(path.image)
```

@@

```{r b_centre_oa, eval = T, message=FALSE, out.height= "60%", out.width="60%"}
#fig.height=4, fig.width=4, 
path.image <- paste0(path, "/outputs/b_dist_centre_oa.png")
knitr::include_graphics(path.image)
```

```{r r_squared, eval=F, results='asis'}
# This is for the RSquared of the different website density regressions.
# The RSquared does not drop much hence it is not worth reporting.

path.in1 <- paste0(path, "/outputs/r2_all_oa.csv")
path.in2 <- paste0(path, "/outputs/r2_all_la.csv")

read.csv(path.in2) %>% #left_join(read.csv(path.in2)) %>% 
  ggplot(aes(x=year)) +
  # geom_line(aes(y=London, color = "OA to London"), size=1) +
  # geom_line(aes(y=cities, color = "OA to nearest city"), size=1) +
  # geom_line(aes(y=retail, color = "OA to nearest retail centre"), size=1) +

  geom_line(aes(y=London.LA, color = "LA to London"), size=1, linetype = 2) +
  geom_line(aes(y=cities.LA, color = "LA to nearest city"), size=1, linetype = 2) +
  geom_line(aes(y=retail.LA, color = "LA to nearest retail centre"), size=1, linetype = 2) +

  scale_color_discrete(name = "R-squared for regression:") +
  scale_linetype_manual(name = "Website density regressions") +
  ylab("R-squared") + 
  ggtitle("Website density regressions") +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5))

@@

# read.csv(path.in2) #%>% left_join(read.csv(path.in2)) %>% 
#   pivot_longer(names_to = "destinations",
#                values_to = "Rsquared",
#                cols = 2:7) %>% 
#   arrange(destinations, year) %>% 
#   ggplot(aes(x=year)) +
#   geom_line(aes(y=Rsquared, group=destinations, colour=destinations)) +
#   geom_textline(aes(y=Rsquared, group=destinations, colour=destinations, 
#                     label=destinations),
#                 hjust = 1) +
#   theme(legend.position = "none") +
#   theme_minimal()

@@

@@

```{r gini_oa, eval=T, results='asis'}
path.in <- paste0(path, "/outputs/gini_oa.csv")

read.csv(path.in) %>% dplyr::select(year, gini.a.n.) %>% 
  ggplot(aes(x=year, y=gini.a.n.)) +
  geom_bar(stat = "identity") + 
  ylab("Gini") +
  theme_minimal() +
  ggtitle("Gini coefficient, number of websites per Output Area") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

@@

```{r gini_la, results='asis'}
path.in <- paste0(path, "/outputs/gini_la.csv")

read.csv(path.in) %>% dplyr::select(year, gini.a.n.) %>% 
  ggplot(aes(x=year, y=gini.a.n.)) +
  geom_bar(stat = "identity") + 
  ylab("Gini") +
  theme_minimal() +
  ggtitle("Gini coefficient, number of websites per Local Auhtority") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

## Spatial attributes, a summary

-   Spatial dependency relatively small and constant over time / scales

-   At local scale, consistent hotspots over time

-   More granular analysis reveals hotspots

@@

@@

-   Plateau overtime

-   Distance effect: urban gravitation increases over time and then
    drops

-   Consistent across scales and definitions of urban

@@

```{r UK S, eval=T, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"}
path.image <- paste0(path, "/outputs/s_uk.png")
knitr::include_graphics(path.image)
```

@@

# Rank dynamics: stability vs. deversity

@@

to do: the same for OAs

------------------------------------------------------------------------
# Conclusions

## What have we learned?

@@

## What have we *yet* to learn?

-   Explain the spatial patterns of fast/slow web adoption

    -   Applied the same analysis fo OA

    -   Survival regressions [@perkins2005international]

-   Expand our definition of web to websites with \# of postcodes \> 1

>>>>

::: {style="margin-left: 50px !important; text-align:left !important"}
-   Introduction
-   Web data
-   Spatial analysis
-   S-shaped diffusion curves
-   Rank dynamics
-   Conclusions <br> <br>
    <!-- [etranos.info/post/gceg2022](https://etranos.info/post/gceg2022/) -->
:::

@@

-   Diffusion of a new technology: the *web*
-   Geographers used to be interested in diffusion
-   @hagerstrand1968innovation
-   Passed the torch to economists and sociologists 
-   Why? Lack of granular data:

@@

-   Observe commercial websites 1996 - 2012 in the UK (*.co.uk*)

-   Geolocate:

    - to a unique postcode

    - to multiple postcodes

-------------------------------------------

```{r , eval=T, message=FALSE, out.width = "1200px"}
path.image <- paste0(path, "/presentations/images/past_publications.png")
knitr::include_graphics(path.image)
```

@@

![](C:/Users/nw19521/OneDrive - University of Bristol/projects/shoreditch/paper/images_screenshots/screenshot_directory_website_2010.png)

@@

![](C:/Users/nw19521/OneDrive - University of Bristol/projects/shoreditch/paper/images_screenshots/screenshot_2010.png)

@@

---

> **Neighbourhood effect**: diffusion proceeds outwards from innovation
> centers, first "hitting" nearby rather than far-away locations
> [@grubler1990rise]

@@

-   Website density regressions -- distance effect

@@

```{r moransi_la, results='asis'}
path.in <- paste0(path, "/outputs/lisa/morani_la.csv")

@@

```{r, eval=T, moransi_oa, results='asis'}
path.in <- paste0(path, "/outputs/lisa/morani_oa.csv")
# read.csv(path.in) %>% dplyr::select(year, morani) %>% 
#   rename('Moran\'s I' = morani,
#          Year = year) %>% 
#   arrange(Year) %>% 
#   kable(digits = 3, 
#         label = "Moran\'s I per year, Output Areas") %>% 
#     kable_classic(full_width = F, html_font = "Cambria")

@@

```{r lisa_la, results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/lisa/")

@@

```{r lisa_oa, eval=T,results='asis', out.width = "30%"}
path.images <- paste0(path, "/outputs/lisa/")

@@

```{r b_London_la, fig.height=5, fig.width=5, message=FALSE}
path.image <- paste0(path, "/outputs/lisa/b_dist_london_la.png")
knitr::include_graphics(path.image)
```

@@

```{r b_city_la, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/lisa/b_dist_city_la.png")
knitr::include_graphics(path.image)
```

@@

```{r b_centre_la,  fig.height=5, fig.width=5,message=FALSE}
#, out.height= "60%", out.width="60%"
path.image <- paste0(path, "/outputs/lisa/b_dist_centre_la.png")
knitr::include_graphics(path.image)
```

@@

```{r b_London_oa, eval=T, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/lisa/b_dist_london_oa.png")
knitr::include_graphics(path.image)
```

@@

```{r b_centre_oa, eval = T,  fig.height=5, fig.width=5,message=FALSE}
#fig.height=4, fig.width=4, 
#, out.height= "60%", out.width="60%"
path.image <- paste0(path, "/outputs/lisa/b_dist_city_oa.png")
knitr::include_graphics(path.image)
```

@@

```{r b_city_oa, eval = T, fig.height=5, fig.width=5, message=FALSE}
#, out.width = "60%"
path.image <- paste0(path, "/outputs/lisa/b_dist_centre_oa.png")
knitr::include_graphics(path.image)
```

```{r r_squared, eval=T, results='asis'}
# This is for the RSquared of the different website density regressions.

path.in1 <- paste0(path, "/outputs/lisa/r2_all_oa.csv")
path.in2 <- paste0(path, "/outputs/lisa/r2_all_la.csv")

# read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>% 
#   ggplot(aes(x=year)) +
#   geom_line(aes(y=London, color = "OA to London"), size=1) +
#   geom_line(aes(y=cities, color = "OA to nearest city"), size=1) +
#   geom_line(aes(y=retail, color = "OA to nearest retail centre"), size=1) +
# 
#   geom_line(aes(y=London.LA, color = "LA to London"), size=1, linetype = 2) +
#   geom_line(aes(y=cities.LA, color = "LA to nearest city"), size=1, linetype = 2) +
#   geom_line(aes(y=retail.LA, color = "LA to nearest retail centre"), size=1, linetype = 2) +
# 
#   scale_color_discrete(name = "R-squared for regression:") +
#   #scale_linetype_manual(name = "Website density regressions111") 
#   ylab("R-squared") + 
#   ggtitle("Website density regressions") +
#   theme_minimal() +
#   theme(axis.title.x=element_blank(),
#         plot.title = element_text(hjust = 0.5))

read.csv(path.in1) %>% left_join(read.csv(path.in2)) %>% 
  pivot_longer(!year, names_to = "regression", values_to = "Rsquared") %>% 
  mutate(LA = if_else(str_ends(regression, ".LA"), " to LA", "to OA"),
         regression = str_remove_all(regression, ".LA"),
         line = paste0(regression, " ", LA)) %>% 
  ggplot() +
  geom_line(aes(x=year, y = Rsquared, color = line),
            size = 1) +
  scale_color_discrete(name = "R-squared for regression:") +
  #scale_linetype_manual(name = "Website density regressions111") 
  ylab("R-squared") + 
  ggtitle("Website density regressions") +
  theme_minimal() +
  theme(axis.title.x=element_blank(),
        plot.title = element_text(hjust = 0.5))

@@

@@

## Neighbourhood effect

- Spatial dependency
	- Relatively small and constant over time / scales
	- London hot spot early on
	- At local scale, consistent hotspots over time
	- Granular analysis reveals other hotspots

- Distance effect
	- Urban gravitation increases over time and then drops
	- Granular analysis: gravitation
	- Lost explanatory power over time

@@

```{r gini_la, results='asis'}
path.in <- paste0(path, "/outputs/lisa/gini_la.csv")

read.csv(path.in) %>% dplyr::select(year, gini.a.n.) %>% 
  ggplot(aes(x=year, y=gini.a.n.)) +
  geom_bar(stat = "identity") + 
  ylab("Gini") +
  theme_minimal() +
  ggtitle("Gini coefficient, websites per firm in Local Auhtority") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

@@

```{r gini_oa, eval=T, results='asis'}
path.in <- paste0(path, "/outputs/lisa/gini_oa.csv")

read.csv(path.in) %>% dplyr::select(year, gini.a.n.) %>% 
  ggplot(aes(x=year, y=gini.a.n.)) +
  geom_bar(stat = "identity") + 
  ylab("Gini") +
  theme_minimal() +
  ggtitle("Gini coefficient, websites per Output Area") +
  theme(plot.title = element_text(hjust = 0.5)) 
```

## Hieararchy

@@

-   Polarisation decreases over time

@@

@@

```{r UK S, eval=T}
#, fig.height=5, fig.width=5, message=FALSE, out.width = "60%"

path.image <- paste0(path, "/outputs/s_uk.png")
knitr::include_graphics(path.image)
```

@@

## Diffusion speed

- Spatial heterogeneity
- Not clear pattern

# Rank dynamics: stability vs. volatility

- Adoption heterogeneity 
- Perceptions of risk and economic returns from new technologies
- Early adopters vs. laggards, leapfrogging

@@

# Conclusions

----

@@

-   Stability and volatility: leapfrogging, early adopters dropping, but also maintaining
